Fluid structure interaction with ETVF

### 2021-05-09 manuscript/paper.tex
Add new dynamic plate example by Turek. Improve boundary condition of pressure

>>>>

\subsection{Dynamics response of an elastic plate}
\label{sec:elastic-plate}

In this example we validate the ETVF scheme in modeling an elastic structure.
This example is taken from \cite{Sun2019study}, who took it from Turek and
Hron, who simulated it using FEM.

An elastic plate is attached to a rigid cylinder. The material properties of
the elastic plate are as follows, the Young's modulus is $1.4\times10^6Pa$ and
a Poisson ratio of $0.4$ and the density is $1000 kg/m^3$. This plate is held
free in a gravity field whose value is $2m/s^2$.
